\textbf{CPSC 504 Project\\\vspace{3 cm}\Huge{An investigation into an application to manage data transformations and updates}\vspace{2 cm}}

### 2015-04-08 Final_Paper/Paper.tex
Draft of Introduction.

\section{Solution}
\subsection{Transformation Language}
\subsection{View Maintenance}
\subsection{Proof of Concept}

>>>>

\section{Solution}
In this project, we focus on three different ways a user can use the application to fetch data.

\noindent

\section{Types of Changes Supported}
\subsection{Transformation Language}
\subsection{View Maintenance}
\subsection{Proof of Concept}
In the proof of concept, we had an extra step that was not included in \cite{arniThesis}. We decided to allow for the user to choose which changes to sync to the remote data source. \textcolor{red}{add screen shots!! Kailang can write about all the cool things she did here!! :)}
